\thesistitle

### 2019-07-23 sections/clonerefactor.tex
High variability

\subsubsection{Convert Equality Array to Graph}
\todo{TODO}
\begin{table}[H]
\begin{center}
 \caption{The equality arrays in our example figure \ref{fig:equalityarrays}.} \label{table:equalityarrays2}
 \medskip
\begin{tabular}{|l|l|l|}
\hline
Node (n) & Equality Array (E) \\ \hline
1        & {[}1, -2, 3, -5, -6{]} \\ \hline
2        & {[}1, -2, 3, -5, -6{]} \\ \hline
3        & {[}8, -2, 4, -5, -6{]} \\ \hline
4        & {[}1, -2, 7, -5, -6{]} \\ \hline
\end{tabular}
\end{center}
\end{table}

>>>>

\subsubsection{Convert Equality Array to Graph}
When a found clone class does not adhere to the global thresholds as explained in the previous section, we need to determine whether it contains any valid subclones.

\begin{figure}[H]
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
doA(a, b, c);
doA();
doB();
doC();
\end{javacode}}
\colchunk[2]{
\begin{javacode}
doB(d, e, f);
doA();
doB();
doC();
\end{javacode}}
\end{parcolumns}
\caption{Variables with different types but the same name.}
\label{fig:2rvariabilityhigh1}
\end{figure}

The first line of the cloned fragment shown in figure \ref{fig:2rvariabilityhigh1} has a high variability with its cloned fragement. However, the rest of this method does not have any variability. The global thresholds could indicate a too high variability and thus render this clone invalid. However, in this case, it might still have a valid subclone.

\todo{TODO}
\begin{table}[H]
\begin{center}
 \caption{The equality arrays in our example figure \ref{fig:equalityarrays}.} \label{table:equalityarrays2}
 \medskip
\begin{tabular}{|l|l|l|}
\hline
Node (n) & Equality Array (E) \\ \hline
1        & {[}1, -2, 3, -5, -6{]} \\ \hline
2        & {[}1, -2, 3, -5, -6{]} \\ \hline
3        & {[}8, -2, 4, -5, -6{]} \\ \hline
4        & {[}1, -2, 7, -5, -6{]} \\ \hline
\end{tabular}
\end{center}
\end{table}
